Best Practices for Alchemical Free Energy Calculations [Article v \versionnumber]

### 2020-11-28 paper/manuscript.tex
version 1.0

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\textbf{ASJSM}: Coordinated the document, contributed to most sections, and co-designed Figs.~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_types_of_networks},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis}, and created Figs.~\ref{fig:fig_what_is_lambda},~\ref{fig:fig_what_is_alchemy},~\ref{fig:overlap},~\ref{fig:pmf} and replotted~\ref{fig:automatic-equilibration-detection} and~\ref{fig:fig_types_of_networks}.\\
\textbf{JS}: Created Figs.~ \ref{fig:fig_what_is_alchemy},~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis}, and an initial draft of~\ref{fig:fig_types_of_networks}. Wrote Sec.~\ref{sec:plot_data}, the checklist Sec.~\ref{sec:checklist}, and contributed to general formatting discussions and editing.\\
\textbf{MK}: Contributed to Sec.~\ref{sec:data_analysis}, provided the data for figure~\ref{fig:overlap}, compiled the dataset for Sec.~\ref{sec:benchmark} and helped edit the paper.\\
\textbf{DLM}: Contributed to the outline, drafted some of the sections, gave ideas on figures, and helped edit the paper.\\
\textbf{GT}: Contributed to Sec.~\ref{sec:intro} and~\ref{sec:drugdiscovery}, and helped edit the paper.\\
\textbf{AR}: Created figure~\ref{fig:freeenergytrajectories}, contributed to sections~\ref{sec:theory} and~\ref{sec:simulation_protocol_choice}, and helped edit the paper.\\
\textbf{MRS}: Helped create figure~\ref{fig:fig_what_is_lambda}, wrote Sec.~\ref{sec:important_path} describing choices for alchemical pathways and parts of~\ref{sec:data_analysis} on the analysis for free energy calculations. Reviewed and edited text throughout.\\
\textbf{LNN}: Helped write the simulation length, stopping conditions, and information saving section. Edited and reviewed alchemical path section.\\
\textbf{BA}: Helped write the uncertainty estimation, stopping conditions, and output analysis sections and created figure ~\ref{fig:convergence_forward_reverse}.\\
\textbf{JM}: Contributed to Sec.~\ref{subsec:reproducible},~\ref{sec:prerequisites},~\ref{sec:important_path},~\ref{subsec:estimators},~\ref{subsec:uncertainty}, and~\ref{sec:conclusion}\\
\textbf{JDC}: Wrote Sec.~\ref{sec:decorrelating-samples} and~\ref{sec:automatic-equilibration-detection} discussed structure and design of the whole document, suggested Figs.~\ref{fig:fig_what_is_alchemy} and~\ref{fig:fig_sampling_scheme} \\
\textbf{HX}: Contributed Sec.~\ref{subsec:accuracy}, to Sec.~\ref{sec:relative-fe-protocol}, and to Sec.~\ref{sec:are-they-good}.\\
\textbf{HBM} Contributed to Sec.~\ref{sec:plot_data} and Fig.~ \ref{fig:scatterplot_analysis} and helped edit the paper.\\
\textbf{SP} Wrote Sec.~\ref{sec:software}.
\textbf{DFH} Contributed to Sec.~\ref{sec:software} and helped edit the paper.
% We suggest you preserve this comment:
For a more detailed description of author contributions,
see the GitHub issue tracking and changelog at \githubrepository.

@@

\section*{Potentially Conflicting Interests}
%%%%%%%
%Declare any potentially competing interests, financial or otherwise
%%%%%%%
JM is a current member of the Scientific Advisory Board of Cresset. 
MK is employed by Cresset who commercially distribute a software for performing alchemical free energy calculations. MRS is a Open Science Fellow and consultant for Silicon Therapeutics.

\section*{Funding Information}
%%%%%%%
% Authors should acknowledge funding sources here. Reference specific grants.
%%%%%%%
ASJSM and JM acknowledge funding through an EPSRC flagship software grant: EP/P022138/1
MK and JM acknowledge funding through Innovate UK by KTP partnership 011120.
AR acknowledges partial support from the Tri-Institutional Program in Computational Biology and Medicine and the Sloan Kettering Institute.
HEBM acknowledges support from a Molecular Sciences Software Institute Investment Fellowship and Relay Therapeutics.
JDC is a current member of the Scientific Advisory Board of OpenEye Scientific Software and a consultant to Foresite Laboratories. A complete funding history for the Chodera lab can be found at \url{http://choderalab.org/funding}.. A complete funding history for the Chodera lab can be found at \url{http://choderalab.org/funding}. 
DLM acknowledges support from the National Institutes of Health (R01GM108889, R01GM124270, and R01GM132386), and the National Science Foundation (CHE 1352608).
JDC acknowledges support from the National Institutes of Health (NIH P30 CA008748, NIH R01 GM121505, R01 GM132386).
The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.

>>>>

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\textbf{ASJSM}: Coordinated the document, contributed to most sections, and co-designed Figs.~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_types_of_networks},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis}, and created Figs.~\ref{fig:fig_what_is_lambda},~\ref{fig:fig_what_is_alchemy},~\ref{fig:overlap},~\ref{fig:pmf} and replotted~\ref{fig:automatic-equilibration-detection} and~\ref{fig:fig_types_of_networks}.\\
\textbf{BA}: Helped write the uncertainty estimation, stopping conditions, and output analysis sections and created figure ~\ref{fig:convergence_forward_reverse}.\\
\textbf{HBM} Contributed to Sec.~\ref{sec:plot_data} and Fig.~ \ref{fig:scatterplot_analysis} and helped edit the paper.\\
\textbf{JDC}: Wrote Sec.~\ref{sec:decorrelating-samples} and~\ref{sec:automatic-equilibration-detection} discussed structure and design of the whole document, suggested Figs.~\ref{fig:fig_what_is_alchemy} and~\ref{fig:fig_sampling_scheme} \\
\textbf{DFH} Contributed to Sec.~\ref{sec:software} and helped edit the paper. \\
\textbf{MK}: Contributed to Sec.~\ref{sec:data_analysis}, provided the data for figure~\ref{fig:overlap}, compiled the dataset for Sec.~\ref{sec:benchmark} and helped edit the paper.\\
\textbf{JM}: Contributed to Sec.~\ref{subsec:reproducible},~\ref{sec:prerequisites},~\ref{sec:important_path},~\ref{subsec:estimators},~\ref{subsec:uncertainty}, and~\ref{sec:conclusion}\\
\textbf{DLM}: Contributed to the outline, drafted some of the sections, gave ideas on figures, and helped edit the paper.\\
\textbf{LNN}: Helped write the simulation length, stopping conditions, and information saving section. Edited and reviewed alchemical path section.\\
\textbf{SP} Wrote Sec.~\ref{sec:software}. \\
\textbf{AR}: Created figure~\ref{fig:freeenergytrajectories}, contributed to sections~\ref{sec:theory} and~\ref{sec:simulation_protocol_choice}, and helped edit the paper.\\
\textbf{JS}: Created Figs.~ \ref{fig:fig_what_is_alchemy},~\ref{fig:fig_binding_thermodynamic_cycle},~\ref{fig:fig_topology},~\ref{fig:fig_mcss},~\ref{fig:fig_absolute_thermodynamic_cycle},~\ref{fig:scatterplot_analysis}, and an initial draft of~\ref{fig:fig_types_of_networks}. Wrote Sec.~\ref{sec:plot_data}, the checklist Sec.~\ref{sec:checklist}, and contributed to general formatting discussions and editing.\\
\textbf{MRS}: Helped create figure~\ref{fig:fig_what_is_lambda}, wrote Sec.~\ref{sec:important_path} describing choices for alchemical pathways and parts of~\ref{sec:data_analysis} on the analysis for free energy calculations. Reviewed and edited text throughout.\\
\textbf{GT}: Contributed to Sec.~\ref{sec:intro} and~\ref{sec:drugdiscovery}, and helped edit the paper.\\
\textbf{HX}: Contributed Sec.~\ref{subsec:accuracy}, to Sec.~\ref{sec:relative-fe-protocol}, and to Sec.~\ref{sec:are-they-good}.
% We suggest you preserve this comment:
For a more detailed description of author contributions,
see the GitHub issue tracking and changelog at \githubrepository.

@@

\section*{Potentially Conflicting Interests}
%%%%%%%
%Declare any potentially competing interests, financial or otherwise
%%%%%%%
JM is a current member of the Scientific Advisory Board of Cresset. 
MK is employed by Cresset who commercially distribute a software for performing alchemical free energy calculations. MRS is a Open Science Fellow and consultant for Silicon Therapeutics.
JDC is a current member of the Scientific Advisory Board of OpenEye Scientific Software and a consultant to Foresite Laboratories.
\section*{Funding Information}
%%%%%%%
% Authors should acknowledge funding sources here. Reference specific grants.
%%%%%%%
ASJSM and JM acknowledge funding through an EPSRC flagship software grant: EP/P022138/1
MK and JM acknowledge funding through Innovate UK by KTP partnership 011120.
AR acknowledges partial support from the Tri-Institutional Program in Computational Biology and Medicine and the Sloan Kettering Institute.
HEBM acknowledges support from a Molecular Sciences Software Institute Investment Fellowship and Relay Therapeutics.
DLM acknowledges support from the National Institutes of Health (R01GM108889, R01GM124270, and R01GM132386), and the National Science Foundation (CHE 1352608).
JDC acknowledges support from the National Institutes of Health (NIH P30 CA008748, NIH R01 GM121505, R01 GM132386).
A complete funding history for the Chodera lab can be found at \url{http://choderalab.org/funding}.
The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.
